\chapter{Environment}\label{chapter:environment}
In this chapter we discuss about the simulating environment that we used or developed in our experiments. It is divided in 3 sections: Server's Referee: the changes we made on HFO's referee; Feature set: the features we chose to receive from HFO's environment; Actions: the output of our Neural Networks; Reward System: the learning conditions to our Neural Networks. 

\section{HFO Server's Referee}
The Half Field Offensive environment has a principle: start an episode with the ball positioned in the middle field. That is not applicable to our real domain. We did some changes in HFO's Server due to this incompatibility of domains:

\begin{itemize}
    \item Half Field Offensive's referee restricts all agents on the right side of the field. Our problem is more complex due to defending on opponent's side as well. Our referee covers the whole field.
    \item Given two areas O and T, opponents spawns randomly on O and the same for teammates on T. We need a spawn similar to a real attack situation in Soccer Simulation 2D. For the defender team We fixed specifics X axis for types of agent and randomizes the Y axis. The midfielders starts in front of the defenders. For the attacking team, is the same logic for attackers and midfielders. We decided to do not randomize the Y axis and fix it on 0 for all attackers.   
    \item The ball always starts near the midfielders of the attacking team in our environment. Doing so, We simulate a counterattack of the opponent.
    \item We use a noise-free server due to the agents initial learning. Once well trained, it can train in a noisy system.
\end{itemize}

\section{Feature Set}
HFO's high-level features set returns many features that is not relevant for our problem, such as opening angle to opponent's goal or pass opening angle to a teammate. We decided to remove those variables for the models understand more easier what to do. Another change was in the normalization of the features. The original environment returned normalized features in relation due to the half field problem. Once our problem is more comprehensive and the agents are in the same space and the features are strict, We maintained the without normalization. 

Let $T$ denote the number of teammates in game and $O$ the
number of opponents. There are a total of $10 + 3T + 2O + 1$ high-level
features in our environment.

\begin{enumerate}[noitemsep]
\setcounter{enumi}{-1}
\item{\textbf{X position} - The agent’s x-position on the field.}
\item{\textbf{Y position} - The agent’s y-position on the field.}
\item{\textbf{Orientation} - The global direction that the agent is facing.}
\item{\textbf{Ball X} - The ball's x-position on the field.}
\item{\textbf{Ball Y} - The ball's y-position on the field.}
\item{\textbf{Able to Kick} - Boolean indicating if the agent can kick the ball.}
\item{\textbf{Goal Center Proximity} - Agent's proximity to the center of the goal.}
\item{\textbf{Goal Center Angle} - Angle from the agent to the center of the goal.}
\item{\textbf{Proximity to Opponent} - If an opponent is present,
  proximity to the closest opponent. Invalid if there are no
  opponents.}
\item [$T$] {\textbf{Proximity from Teammate i to Opponent} - For each
  teammate i: the proximity from the teammate to the closest
  opponent. This feature is invalid if there are no opponents or if
  teammates are present but not detected.}
\item [$2T$] {\textbf{X, Y of Teammates} - For each teammate: the x-position, y-position.}
\item [$2O$] {\textbf{X, Y of Opponents} - For each opponent: the x-position, y-position.}
\item [$+1$] {\textbf{Interceptable} - Whether the agent can intercept the ball or
 not.}
\end{enumerate}

\section{Actions}
Based on \cite{cyrus}, We chose four actions: 
\begin{enumerate}
    \item Move: Performs the basic move, going to the position according to the formation file.
    \item Go to ball: Performs an interception move, tackling the opponent when it can.
    \item Defend Goal: Goes to the circumcenter position of the triangle goalie position, right or left goal post position and attacker position.
    \item Block: Performs \cite{marlik2011}'s Marlik Block.
\end{enumerate}

We decided to choose Marlik's block over Cyrus' due to Cyrus' harassment and effectiveness. Cyrus' block is too advanced and that induces great chances of a dribble and then a goal. 

\section{Reward System}
The reward system is also very similar to \cite{cyrus}'s. We just removed the cycles condition. We tried to adapt \cite{tgze}'s ball potential equation to Soccer Simulation 2d domain to be a reward as well but it did not fit in our experiments.